\textbf{Autoreduction - an automated data reduction system for beam instruments}

### 2016-09-22 Documentation/paper/paper.tex
Fixing architecture wrt queue.

\begin{itemize}[noitemsep]
\item
  A listener for new jobs
\item
  The state database \& coordinator
\item
  Workers for reduction processing
\end{itemize}

When the listener detects that a new job should be created, it sends a
request to do so to \emph{Data Ready}. The state database consumes the
request and creates the corresponding job in the database, before
sending a request to process it to \emph{Reduction Pending}. A reduction
worker takes this message and runs the appropriate script, sending the
result to either \emph{Reduction Complete} or \emph{Reduction Error},
where it's consumed by the state database to update the status of the
run.

\begin{figure*}
\centering\includegraphics[width=1.15\linewidth,angle=90,origin=c]{system.png}
\caption{How the autoreduction system fits into the ISIS workflow.}
\end{figure*}

@@

The system is deployed at ISIS, in limited use. The frontend node,
serving the message queue as well as managing the state and web app, is
a Windows Server system running on a Hyper-V\cite{hyper-v} virtualisation
cluster; it serves the web app using Microsoft's Internet Information
Services (IIS)\cite{iis} and FastCGI\cite{fcgi}. There is one reduction node, 
running Red Hat Enterprise Linux 7\cite{rhel} on a dedicated server -- 
reducing large amounts of data is very CPU-intensive.

@@

\begin{enumerate}
\item
  Expanding the system to accommodate greater volume of use -- this
  might involve adding more reduction workers, for example.
\item
  Integrating other methods of listening for new runs -- the current
  method of watching a file archive is specific to ISIS.
\item
  Improving portability and deployability of the current software; the
  state database/webapp in particular is currently unsupported for
  Linux, and the whole system is somewhat nontrivial to deploy even to a
  development environment.
\end{enumerate}

>>>>

\begin{itemize}[noitemsep]
\item
  A listener for new jobs
\item
  The state database \& coordinator
\item
  A worker for reduction processing
\end{itemize}

When the listener detects that a new job should be created, it sends a
request to do so to \emph{Data Ready}. The state database consumes the
request and creates the corresponding job in the database, before
sending a request to process it to \emph{Reduction Pending}. The reduction
worker takes this message and runs the appropriate script, sending the
result to either \emph{Reduction Complete} or \emph{Reduction Error},
where it's consumed by the state database to update the status of the
run.

\begin{figure*}
\centering\includegraphics[width=1.15\linewidth,angle=90,origin=c]{system.png}
\caption{How the current autoreduction system fits into the ISIS workflow.}
\end{figure*}

@@

The system is deployed at ISIS, in limited use. The frontend node, managing
the state and web app, is a Windows Server system running on a 
Hyper-V\cite{hyper-v} virtualisation cluster; it serves the web app using
Microsoft's Internet Information Services (IIS)\cite{iis} and 
FastCGI\cite{fcgi}.

There is one reduction node, running Red Hat Enterprise Linux 7\cite{rhel}
on a dedicated server -- reducing large amounts of data is very CPU-intensive.
This node also serves the message queue; subsequent worker nodes would
not have multiple message queues, and it would be wise to separate the
message queue from the worker entirely in this case.

@@

\begin{enumerate}
\item
  Expanding the system to accommodate greater volume of use -- this
  might involve accomodating more reduction workers, for example.
\item
  Integrating other methods of listening for new runs -- the current
  method of watching a file archive is specific to ISIS.
\item
  Improving portability and deployability of the current software; the
  state database/webapp in particular is currently unsupported for
  Linux, and the whole system is somewhat nontrivial to deploy even to a
  development environment.
\end{enumerate}
